A global compilation reveals divergent biomass partitioning between plant functional types

### 2014-10-24 manuscript/draftpaper.Rnw
fig SI-8 updated

We found some evidence for a higher root-shoot ratio ($M_R/M_T$) in deciduous angiosperms (Fig.~\ref{fig:figureSI2}), however differences were small and depended on plant height. We found near-isometric scaling ($M_R \propto H^{0.93}$) (cf. \cite{hui_near_2014, cairns_root_1997}), leading to only small shifts in the root-shoot ratio with increasing height. We did not test for direct climate effects on $M_R/M_T$ due to limited data availability for root biomass.

>>>>

We found some evidence for a higher root-shoot ratio ($M_R/M_T$) in deciduous angiosperms (Fig.~\ref{fig:figureSI2}), however differences were small and depended on plant height. We found near-isometric scaling ($M_R \propto H^{0.93}$) \cite{hui_near_2014, cairns_root_1997, mokany_critical_2006}, leading to only small shifts in the root-shoot ratio with increasing height. We found no effects of climate on root-shoot ratio, consistent with a recent global comparison \cite{mokany_critical_2006}. Relation precip to root biomass is probably more complex \cite{schenk_rooting_2002}.
